Notes on Wide Gap

### 2016-04-12 paper/wide_gap_notes.tex
math notes url changed
thin gap limit of curl

\newcommand{\uphi}{\ensuremath{u_\phi}}
\newcommand{\rhat}{\ensuremath{\mathbf{\hat{r}}}}
\newcommand{\phihat}{\ensuremath{\mathbf{\hat{\phi}}}}
\newcommand{\zhat}{\ensuremath{\mathbf{\hat{z}}}}

@@

@@

Everything here follows \url{http://farside.ph.utexas.edu/teaching/336L/Fluidhtml/node177.html#scyl}.

>>>>

\newcommand{\uphi}{\ensuremath{u_\phi}}
\newcommand{\rhat}{\ensuremath{\mathbf{\hat{r}}}}
\newcommand{\phihat}{\ensuremath{\mathbf{\hat{\phi}}}}
\newcommand{\zhat}{\ensuremath{\mathbf{\hat{z}}}}
\newcommand{\xhat}{\ensuremath{\mathbf{\hat{x}}}}
\newcommand{\yhat}{\ensuremath{\mathbf{\hat{y}}}}

@@

Another operator we need is the curl $\nabla \times \mathbf{A}$,

\beq
\nabla \times \mathbf{A} = -\partial_{\widetilde{z}} A_\phi \rhat + \left(\partial_{\widetilde{z}} A_r - \partial_{\widetilde{r}} A_z \right) \phihat + \frac{1}{\widetilde{r}} \partial_{\widetilde{r}} \left( \widetilde{r} A_\phi\right) \zhat
\eeq

\beq
= - \frac{1}{\delta} \partial_z A_\phi \rhat + \left(\frac{1}{\delta} \partial_z A_r - \frac{1}{\delta} \partial_x A_z\right) \phihat + \left(1 - \delta x\right) \frac{1}{\delta} \left(\partial_x A_\phi + \delta A_\phi + \delta x \partial_x A_\phi \right) \zhat
\eeq

Taking $\lim\limits_{\delta \to 0}$ of the above and changing variables $\phi \to y$, etc., we get

\beq
\nabla \times \mathbf{A} = -\partial_z A_y \xhat + \left(\partial_z A_x - \partial_x A_z\right) \yhat + \partial_x A_y \zhat
\eeq

@@

Everything here follows \url{http://farside.ph.utexas.edu/teaching/336L/Fluidhtml/node257.html}.
